---
title: "Week 10 Day 1 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggfortify)
library(broom)
```

MVP

The file project_management.csv contains data sampled from the recent work schedule of a small construction company. Column estimated_length contains the estimated length of a building job in days, while column actual_length contains the actual recorded length of the job in days.

We are interested in determining the accuracy of the job estimations made by the company using simple linear regression, so we will eventually want to run a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable.


Load the data into a dataframe project
```{r}
project_management <- read_csv("data/project_management.csv")
```

Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.
```{r}
project_management %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```

Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.
```{r}
cor(project_management$estimated_length, project_management$actual_length)
```

Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.
```{r}
project_model <- lm(actual_length ~ estimated_length, project_management)

# estimated_length is a FUNCTION of actual, ie it depends on the actual length, hence why it is first

# after reading answers - it is the OTHER way around.
# if estimated_length is a FUNCTION OF actual_length, actual_length is stated FIRST
# just like, if height is a FUNCTION of weight, it will be (height ~ weight)
```

Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?
```{r}
summary(project_model)
janitor::clean_names(tidy(project_model))
janitor::clean_names(glance(project_model))

# r2 - is coefficient of determination
# the proportion of the variation in the outcome variable that can be explained by variation in the explanatory variable
# the higher r2, the better the line fits the data (but not necessarily causes!!)

# the other important ones to note from here are:
# term, which labels the coefficients
# estimate, which contains the fitted values
# p_value, which contains the p_value for a hypothesis test of that coefficient

```
In this case, r2 is 65% - there is a good fit of the line, but it isn't very high.

the object estimated_length, and, estimate = regression. So 1.22 is the regression number.

Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).
```{r}
autoplot(project_model)
```

Is it statistically significant?

No. It is above 0.05 (on both counts).
