---
title: "R Notebook"
output: html_notebook
---

Building an explantory model


```{r}
library(tidyverse)
library(car)
library(modelr)
library(GGally)

house_data <- read_csv("data/kc_house_data.csv")
```

Q1 - Tidy up the data

```{r}
clean_house_data <- house_data %>%
  select(-c("id", "date", "zipcode", "sqft_living15", "sqft_lot")) %>%
  mutate(waterfront = as.logical(waterfront),
         renovated = as.logical(yr_renovated)) %>%
  mutate(condition = as.factor(condition),
         grade = as.factor(grade))
```

Q3  - use alias to check for aliased variables, and then remove these
```{r}
alias(price ~ ., data = clean_house_data)
```
So, I can see that:

sqft_basement is interacting with sqft_living positively
sqft_basement is interacting with sqft_above negatively


sqft_basement can be computed from just sqft_living - sqft_above.

The answers suggest to drop only sqft_living, I would probably have dropped both living and above. 

```{r}
clean_house_data <- clean_house_data %>%
  select(-sqft_living)

```

Q4 - build model manually and systematically, to include up to four main effects.
```{r}
clean_house_data %>%
  select_if(is.numeric) %>%
  ggpairs()

# from these, I would include:
# bathroom
# sqft_above (highest)

houses_tidy_nonnumeric <- clean_house_data %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- clean_house_data$price

ggpairs(houses_tidy_nonnumeric)
# from these, I would include
# grade
# waterfront

```

So my choices are

sqft_above
bathroom
grade
waterfront


Plot them in these order:

grade (but try my other ones)


then add in bathroom

sqft_above

waterfront


