---
title: "R Notebook"
output: html_notebook
---

Week 11 Day 2 Homework

Decision Trees

In this homework we will create a decision tree to see which factors are useful in predicting whether or not a passenger on the titanic will survive.

Run the code below before you begin:
```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(janitor)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

1 MVP
# 1.1 Question 1
Cleaning up the data is always the first step. Do the following:

- Take only observations which have a survived flag (i.e. that aren’t missing)
- Turn your important variables into factors (sex, survived, pclass, embarkation)
- Create an age_status variable which groups individuals under (and including) 16 years of age into a category called “child” category and those over 16 into a category called “adult”.
- Drop the NA
- Drop any variables you don’t need (X1, passenger_id, name, ticket, far, cabin)

If you need help doing this, the code is below, but please try it yourself first so you can learn!

```{r}
titanic_clean <- titanic_set %>%
  clean_names() %>%
  filter(!is.na(survived)) %>%
  mutate(sex = as.factor(sex),
         survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")),
         port_embarked = as.factor(embarked)) %>%
  mutate(age_status = as.factor(if_else(age <= 16, "child", "adult"))) %>%
  rename(sibling_spouses = "sib_sp",
         parent_children = "parch") %>%
  select(sex, survived_flag, class, port_embarked, age_status, sibling_spouses, parent_children) %>%
  na.omit()

```


# 1.2 Question 2
Have a look at your data and create some plots to ensure you know what you’re working with before you begin. Write a summary of what you have found in your plots. Which variables do you think might be useful to predict whether or not people are going to die? Knowing this before you start is the best way to have a sanity check that your model is doing a good job.

```{r}
head(titanic_clean)
```

```{r}
summary(titanic_clean)
```

```{r}
titanic_clean %>%
  ggplot(aes(x = survived_flag)) +
  geom_bar()
```
This is a pretty good plot to start out with, the ratio of surviving vs not. 

```{r}
titanic_clean %>%
  ggplot(aes(x = survived_flag, fill = class)) +
  geom_bar(position = "dodge")
```

```{r}
titanic_clean %>%
  ggplot(aes(x = survived_flag, fill = sex)) +
  geom_bar(position = "dodge")
```

```{r}
titanic_clean %>%
  ggplot(aes(x = survived_flag, fill = age_status)) +
  geom_bar(position = "dodge")
```

```{r}
titanic_clean %>%
  ggplot(aes(x = survived_flag, fill = port_embarked)) +
  geom_bar(position = "dodge")
```

So from my data exploration, it seems that the variables which indicate a higher probability of survival are:
- Having a ticket for the upper class
- Being female
- Being an adult
- Embarking in Southampton

Equally, the variables which show the probabilities of dying are:
- Having a ticket for the lower class
- Being male
- Being an adult
- Interestingly, also embarking in Southampton

# 1.3 Question 3
Now you can start to build your model. Create your testing and training set using an appropriate split. Check you have balanced sets. Write down why you chose the split you did and produce output tables to show whether or not it is balanced.
[Extra - if you want to force balanced testing and training sets, have a look at the stratified() function in package splitstackshape (you can specify multiple variables to stratify on by passing a vector of variable names to the group argument, and get back testing and training sets with argument bothSets = TRUE)]


```{r}
set.seed(15)

n_data <- nrow(titanic_clean)
test_index <- sample(1:n_data, size = n_data*0.2)
titanic_test <- slice(titanic_clean, test_index)
titanic_train <- slice(titanic_clean, -test_index)
```

```{r}
titanic_test %>%
  janitor::tabyl(survived_flag)
```

```{r}
titanic_train %>%
  janitor::tabyl(survived_flag)
```
I started at a seed of 15 (because I had to start somewhere). This created a test/train split which was pretty well balanced, the proportions are pretty much the same.



# 1.4 Question 4
Create your decision tree to try and predict survival probability using an appropriate method, and create a decision tree plot.

```{r}
titanic_tree <- rpart(
  formula = survived_flag ~ .,
  data = titanic_train,
  method = 'class'
)

rpart.plot(titanic_tree,
           yesno = 2,
           fallen.leaves = TRUE,
           faclen = 6,
           digits = 4)
```

no = dying
yes = surviving

# 1.5 Question 5
Write down what this tells you, in detail. What variables are important? What does each node tell you? Who has the highest chance of surviving? Who has the lowest? Provide as much detail as you can.

The important variables are sex, class, age_status, and sibling_spouses. 

At the first node, the data is split into two groups, male/not, 41% is the chance of dying, and 100% is the amount of data that has been passed through.

Where sex is not male, there is a 76% chance of dying. This then looks at whether class = Lower. Where no, there is a 43% chance of dying.

Where sex is male, there is a 21% chance of dying. This then looks at whether the class = lower, middle. Where yes, there is a 15% chance of dying. 

The highest chance of dying are those where sex = male, class = lower, middle, and where age_status =/= adult; there is a 45.71% chance of dying.
Those with the highest chance of surviving are those where sex =/= male, and where class =/= lower; there is a 96.85% chance of not dying. 


# 1.6 Question 6
Test and add your predictions to your data. Create a confusion matrix. Write down in detail what this tells you for this specific dataset.

```{r}
library(modelr)
library(yardstick)

titanic_test_pred <- titanic_test %>%
  add_predictions(titanic_tree, type = "class")

conf_mat <- titanic_test_pred %>%
  conf_mat(truth = survived_flag, estimate = pred)
conf_mat

titanic_test_pred %>%
  specificity(truth = survived_flag, estimate = pred)
titanic_test_pred %>%
  sensitivity(truth = survived_flag, estimate = pred)
```

TPR - prob of someone surviving
TNR - prob of someone not surviving

Sensitivity and specificity depend on the question that you're setting, i.e. we are trying to predict the probability of someone not dying. 