---
title: "R Notebook"
output: html_notebook
---

Week 10 - Weekend Homework - Model Building

Investigate the avocado dataset, in particular, the AveragePrice of avocados.

Focus on either explanatory, or predictive model.

As part of MVP, to not just run the code and build the model, but also interpret results and write thinking and comments in the script.

```{r}
# reading in libraries

library(tidyverse)
library(modelr)
library(GGally)
library(janitor)
library(lubridate)
```

```{r}
# reading in data

avocado <- read_csv("data/avocado.csv")

avocado <- avocado %>%
  clean_names()

# cleaning the variable names
```

```{r}
# exploring the data

# 4046 - is total number of avocados with PLU 4046 sold
# 4225 - same
# 4770 - same

summary(avocado)
# there doesn't appear to be missing values

avocado %>%
  filter(x_large_bags == 0.00)
# there are 12048 of these obsverations - worth bearing in mind

avocado %>%
  distinct(region)
# there are 54 distinct values in this category - worth bearing in mind

avocado %>%
  distinct(type)
# this can be converted to column type "organic" and then TRUE/FALSE

# date won't be needed, but the month can be extracted from this.

```


```{r}
# changing the type column to is_organic, and restructuring the data to match.
# extracting the month from the date and dropping the date column
# renaming the number columns - from experience, having columns start with x can be problematic in analysis
# I have also come back and renamed these when beginning the model, as it is
# unable to accept the names of variables as numbers, so to make life easier
# as I'm renaming them anyways, I've renamed them with characters

clean_avocado <- avocado %>%
  mutate(month = month(date, label = FALSE, abbr = FALSE),
         is_organic = if_else(type == "organic", TRUE, FALSE)
         ) %>%
  select(-c("date", "type")) %>%
  rename("four_046" = x4046,
    "four_225" = x4225,
    "four_770" = x4770)

```

I will attempt to build an explanatory model.

Steps

Use ggpairs() to explore correlations (grouped, if need be)
I will probably exclude region to begin with, as there are too many possibilities under this
Choose my initial predictors
Select a predictor, and build the first model
Use summary() to explore the stats
Use par(mfrow = c(2, 2)) and plot() to check the plots
Check these for my first options and make my final selection for my first one
Run ggpairs() again to select my second predictor, excluding the first predictor I added in
Build the model
Use par(mfrow = c(2, 2)) and plot() to check the plots
Check these for my first options and make my final selection for my first one
Use anova() to check for statistical significance / difference
Repeat, until I have added 3 / 4

```{r}
clean_avocado %>%
  select(-region) %>%
  ggpairs()
```

It's a bit hard to read from this graph / overview, but the following ones could be good indicators:
volume
4046
4225
4770
total
small
large
x_large
month

Slimming it down a bit to look again, and be able to see better
```{r}
clean_avocado %>%
  select(-c("x1", "region", "year", "is_organic")) %>%
  ggpairs()
```

Now I can see that the follow indicators are good:
total_volume
four_046 (this has the highest, so this will be my first choice)
four_225
four_770
total_bags
small_bags
large_bags

Month may be good, but it's very in between.

x_large_bags is not good.

Getting a closer look at is_organic
```{r}
clean_avocado %>%
  select(average_price, is_organic) %>%
  ggpairs()
```
There appears to be some variation in this graph, so this is also a good one to go for.


Time to build the first model.
```{r}
model_1_a <- lm(average_price ~ four_046, data = clean_avocado)
model_1_a
```

```{r}
summary(model_1_a)
```
From these statistics, what can be inferred is that there is a good p-value (under 0.05) so the model is statistically significant, but it also only accounts for 4.3% of the variation, which is very low.

```{r}
par(mfrow = c(2, 2))
plot(model_1_a)
```
The diagnostic plots also aren't very good - the QQ plot is in a straight line, but in the residuals vs fitted, there are two clear groups (which is also seen in the scale/location plot). Time to try a different variable.

I'll go back and look at the total_volume; the above variable is quite specific, so it could very well be throwing the model off.
```{r}
model_1_b <- lm(average_price ~ total_volume, data = clean_avocado)
model_1_b
```

Checking the summary of the 2nd model
```{r}
summary(model_1_b)
```
This model is also statistically significant, but account for even less than the previous, only 3.7% here.

Checking the diagnostic plots
```{r}
par(mfrow = c(2, 2))
plot(model_1_b)
```
This is no better. There still appears to be two distinct groups.

I will check the is_organic variable.
```{r}
model_1_c <- lm(average_price ~ is_organic, data = clean_avocado)
model_1_c
```

```{r}
summary(model_1_c)
```
This is the best variation I have uncovered so far, accounting for 37.9% of the variation, and the model is also statistically significant.

I will proceed to check the diagnostic plots.
```{r}
par(mfrow = c(2, 2))
plot(model_1_b)
```
There are still two distinct groups in residual vs fitted, and scale v location - but the QQ plot looks pretty well fitted.

As this is the best accounting for variation I have found so far, I will proceed with this model.


I will now progress with adding the second variable, i.e. building the second part onto the model.
To do so, I will begin with exploring the correlations in ggpairs again (and in this, removing is_organic, which has already been used, and region, which has too many)

```{r}
clean_avocado %>%
  select(-c("x1", "region", "is_organic")) %>%
  ggpairs()

```
It's a similar story, the following look good to explore:
total_volume
four_046
four_225
four_770
total_bags
small_bags
large_bags
x_large_bags

In this case, I will begin with total_volume and four_046

```{r}
model_2_a <- lm(average_price ~ is_organic + total_volume, data = clean_avocado)
model_2_a
```

Checking the summary and diagnostic plot
```{r}
summary(model_2_a)
```
The model is still statisticall significant, but the variation covered has only gone up incrementally from the first model.

```{r}
par(mfrow = c(2, 2))
plot(model_2_a)
```
Looking at the diagnostic plots, there are now 3 distinct groups, and it is more evident that the model struggles as the values get higher (can be seen in residuals v fitted). The QQ plot still doesn't look too bad though.


I will now look at the four_046
```{r}
model_2_b <- lm(average_price ~ is_organic + four_046, data = clean_avocado)
model_2_b
```

Looking at the summary stats for this plot
```{r}
summary(model_2_b)
```
This is marginally better; 38.43 vs 38.19.

I will check the diagnostic plots
```{r}
par(mfrow = c(2, 2))
plot(model_2_b)
```
This is the same story as total_volume.

I will check month to see if this has any impact on the performance of the model, as it seems that this model does not response well to continuous variables.

```{r}
model_2_c <- lm(average_price ~ is_organic + month, data = clean_avocado)
model_2_c
```
Checking the summary statistics
```{r}
summary(model_2_c)
```
Surprisingly, this does increase the r-sq value somewhat, and it also remains statistically significant.

I will now check the diagnostic plots.
```{r}
par(mfrow = c(2, 2))
plot(model_2_c)
```
There is good, and bad news in this plot. There are still two distinct groups in the model, however the spread across the y axis in the residual v fitted has resolved and they are better distributed. The downside is, the residuals v leverage plot is not looking as good.


Nonetheless, I will proceed with these two variables. Prior to doing so, I will check them against the single variable, using anova.
```{r}
anova(model_1_c, model_2_c)
```
This is also positive, the model is remaining statistically significant, with the added variable. I will proceed with these two (is_organic + month)


Similarly to going on to the 2nd variable, I will check the ggpairs again.

```{r}
clean_avocado %>%
  select(-c("x1", "region", "is_organic", "month")) %>%
  ggpairs()

```
The correlation with year appears low; however, I do wonder whether this will be different if this is implemented in the model.
Aside from this, the remainders remain the same, so I will consider adding:
year
total_volume
total_bags


First build of third part of model
```{r}
model_3_a <- lm(average_price ~ is_organic + month + year, data = clean_avocado)
model_3_a
```

Checking summary stats
```{r}
summary(model_3_a)
```
Similarly to month, year had a relatively good impact on the model - it increased from 40.57% to 42.1%, while remaining statistically significant.

Checking the plots
```{r}
par(mfrow = c(2, 2))
plot(model_3_a)
```
This has improved on the distribution in res v fitted, and has also improved the res v leverage plot. This is a strong contender.


Next I will add total_volume.
```{r}
model_3_b <- lm(average_price ~ is_organic + month + total_volume, data = clean_avocado)
model_3_b
```

Checking summary stats
```{r}
summary(model_3_b)
```
This only marginally increases the model from 2_c (from 40.5 to 40.7).

Checking the plots
```{r}
par(mfrow = c(2, 2))
plot(model_3_b)
```
This improves residuals v leverage greatly compared to 3_a, but otherwise does not have the same benefits. This may be an option for a 4th variable.

I will lastly check total_bags
```{r}
model_3_c <- lm(average_price ~ is_organic + month + total_bags, data = clean_avocado)
model_3_c
```

Checking summary stats
```{r}
summary(model_3_c)
```
This has the same stats as model 3_b

Checking the plots
```{r}
par(mfrow = c(2, 2))
plot(model_3_c)
```
This is also similar to model 3_b. 

Before settling on year, I will check the anova.
```{r}
anova(model_2_c, model_3_a)
```
This confirms that 3_a is statistically significant compared to 2_c, so I will progress with this model, which is:
is_organic + month + total_bags

As I now have 3 variables in my model, I need to be cautious of overfitting, so I will begin to watch the adjusted r2 values relative to the r2 values.

I feel confident in saying that the options I can explore are:
total_volume
four_046


First build of fourth part of model
```{r}
model_4_a <- lm(average_price ~ is_organic + month + year + total_volume, data = clean_avocado)
model_4_a
```

Checking summary stats
```{r}
summary(model_4_a)
```
There is again only 0.2 improvement (42.34 from 42.1).

Checking plots
```{r}
par(mfrow = c(2, 2))
plot(model_4_a)
```
This is similar to the previous one with total_volume, improvement in res v leverage.

I will now check four_046
```{r}
model_4_b <- lm(average_price ~ is_organic + month + year + four_046, data = clean_avocado)
model_4_b
```


Summary stats
```{r}
summary(model_4_b)
```
This is an improvement of .4, but the adjusted r2 has begun declining in the r2; 42.55 / 42.53 vs 42.1 / 42.09 in model 3_a. This indicates that the model is overfitting.

For comprehension, I will check the plots.
```{r}
par(mfrow = c(2, 2))
plot(model_4_b)
```
These plots are still not as strong as they were in model 3_a. Now there is a split in two groups, and the funnel in res v fitted has returned.

There is one final option to consider to add to this model which are regions, which I will attempt - although there are many, and the model may struggle with these, I will explore this for the sake of completeness.
```{r}
model_4_c <- lm(average_price ~ is_organic + month + year + region, data = clean_avocado)
model_4_c
```

Summary stats
```{r}
summary(model_4_c)
```
This improves the model's r-squared rating, quite significantly, to 58.91. Additionally, many of the regions are statistically significant, some not - to check if they are overall, as a group, I will compare to 3_a using anova.

```{r}
anova(model_3_a, model_4_c)
```
This confirms that model_4_c is statistically significant compared to model 3_a.

As a final check, I will explore the plots.

```{r}
par(mfrow = c(2, 2))
plot(model_4_c)
```
This is an excellent distribution across res v fitted, and the same for scale v location. There is some tail off on the QQ plot, but on the whole, it fits the normal distribution.
The model doesn't seem to fit the res v leverage plot great, but the other plots are strong enough to counter-balance, from my perspective.

Therefore, my final explanatory model, is:

lm(formula = average_price ~ is_organic + month + year + region, 
    data = clean_avocado)

