---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```


Background
QikBit is a start-up company producing low cost fitness trackers. Their flagship product, the KwikBit Unit1 (spot the mistake on the patent form) reproduces the functionality of the best-in-class commercial fitness trackers, but is cheap to make. They are currently preparing to pitch to a potential investor and require a selection of charts to include in their presentation and promotional materials.

```{r}
qb_revenue_breakdown <- CodeClanData::qb_revenue_breakdown
qb_monthly_sales <- CodeClanData::qb_monthly_sales
qb_competitors <- CodeClanData::qb_competitors
qb_device_data <- CodeClanData::qb_device_data
```


Q1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
qb_revenue_breakdown %>%
  ggplot(aes(x = Year, y = Revenue, fill = Product)) +
  geom_bar(stat = "identity")
```

Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).
```{r}
qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow))

```

Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow))

```

Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
qb_competitors %>%
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company))

```

Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
qb_competitors %>%
  ggplot() +
  geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue))

```

Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.
```{r}
qb_device_data %>%
  ggplot() +
  geom_line(aes(x = hours, y = counts, colour = device)) +
  facet_wrap(~ device, nrow = 4)

# answer:

qb_device_data <- 
mutate(qb_device_data, decimal_hour = hours + (mins/60))

ggplot(qb_device_data) +
  aes(x = decimal_hour, y = counts) +
  geom_line() + 
  facet_grid(id ~ device)
```


Take the plots that you produced in part one and now polish them by:
Adding appropriate labels

Answer for Part 2.2
```{r}
theme_qb <- 
  theme(
    text = element_text(size = 12),
    title = element_text(size = 14),
    axis.text = element_text(size = 10),
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(colour = "grey90", linetype = "dashed")
  )
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

# It is NOT possible to set the colour scheme in the theme


ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = Product) +
  geom_col() +
  scale_fill_manual(values = col_scheme) +
  ggtitle(
    "Breakdown of QikBit Revenue by Product Line",
    subtitle =  "2018 and 2019"
  ) +
  theme_qb

#this answer uses the theme and colour scheme
ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = Product) +
  geom_col() +
  scale_fill_manual(values = col_scheme) +
  ggtitle(
    "Breakdown of QikBit Revenue by Product Line",
    subtitle =  "2018 and 2019"
  ) +
  theme_qb

```

```{r}
# Q1. 
qb_revenue_breakdown %>%
  ggplot(aes(x = Year, y = Revenue, fill = Product)) +
  geom_bar(stat = "identity") +
  labs(y = "Sources of revenue")

#Q2
qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  labs(x = "Year", y = "Monthly revenue of Kwikbit Unit 1")

#Q3 
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  labs(x = "Year", y = "Monthly amount")

#q4
qb_competitors %>%
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company)) +
  labs(y = "Annual sales")

#q5
qb_competitors %>%
  ggplot() +
  geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue))
# no change made

#q6
qb_device_data %>%
  ggplot() +
  geom_line(aes(x = hours, y = counts, colour = device)) +
  facet_wrap(~ device, nrow = 4) +
  labs(x = "hours used per day", y = "daily stepcount")


```

Changing the scales and coordinates when appropriate.
```{r}
# Q1. 
qb_revenue_breakdown %>%
  ggplot(aes(x = Year, y = Revenue, fill = Product)) +
  geom_bar(stat = "identity", width =.4) +
  labs(y = "Sources of revenue")

#q2.
qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  ylim(300, 700)+
  labs(x = "Year", y = "Monthly revenue of Kwikbit Unit 1")

#Q3 
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  ylim(1000, 3000)
  labs(x = "Year", y = "Monthly amount")

#q4
qb_competitors %>%
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company)) +
  labs(y = "Annual sales")
# no change

#q5
qb_competitors %>%
  ggplot() +
  geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue))
# no change

#q6 was already amended.


```
Applying a unified theme, which is described below:
    Graphs should have white backgrounds, and use colour sparingly.
    There should be faint grid lines.
    Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
    All plots should use colours from the following company colour scheme.
    col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
theme(panel.background = element_rect(fill = "white", colour = NA))
theme(panel.grid.major = element_line(colour = "light grey")) +
theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25))
```

```{r}
# Q1. 
qb_revenue_breakdown %>%
  ggplot(aes(x = Year, y = Revenue, fill = Product)) +
  geom_bar(stat = "identity", width =.4) +
  scale_fill_manual(
    values = c("Accessories" = "#E89FE9",
                "Smart Watches" = "#50434F",
                "Subscription Services" = "#B6A7B5",
                "Trackers" = "#F9A472"))
  labs(y = "Sources of revenue") +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))
  
#Q2
qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow), colour = "#E89FE9") +
  ylim(300, 700)+
  labs(x = "Year", y = "Monthly revenue of Kwikbit Unit 1") +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))

#Q3 
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  ggplot() +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  scale_fill_manual(values = c("Cost" = "#E89FE9",
                "Total Revenue" = "#50434F"))
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))

  # colour doesn't run

#q4
qb_competitors %>%
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company)) +
  scale_fill_manual(
    values = c("Competitor 1" = "#E89FE9",
                "Competitor 2" = "#50434F",
                "Competitor 3" = "#B6A7B5",
                "Competitor 4" = "#F9A472"))+
  labs(y = "Annual sales") +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))


#q5
qb_competitors %>%
  ggplot() +
  geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue))+
  scale_fill_manual(
    values = c("Competitor 1" = "#E89FE9",
                "Competitor 2" = "#50434F",
                "Competitor 3" = "#B6A7B5",
                "Competitor 4" = "#F9A472")) +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))

# colour doesn't run

#q6
qb_device_data %>%
  ggplot() +
  geom_line(aes(x = hours, y = counts, colour = device), colour = "#E89FE9") +
  facet_wrap(~ device, nrow = 4) +
  labs(x = "hours used per day", y = "daily stepcount") +
  theme(panel.background = element_rect(fill = "white", colour = NA)) +
  theme(panel.grid.major = element_line(colour = "light grey")) +
  theme(panel.grid.minor = element_line(colour = "light grey", size = 0.25)) +
  theme(axis.title = element_text(size = rel(1.0))) +
  theme(axis.title.x = element_text(size = rel(0.7))) +
  theme(axis.title.y = element_text(size = rel(0.7)))

# DONE

```

    
3 Extension
Question 1.
Try out different ways of plotting these three datasets. Which graphs do you think are particularly effective at showing QikBit’s success?  
```{r}

```






